fl0w - a development environment for the\\ KIPR Wallaby

### 2017-03-30 paper.tex
Improved disc0very section, added figure and error recovery

\subsection{disc0very}
disc0very is the networked controller discovery protocol of fl0w\cite{fl0w:Philip Trauner}. It utilizes UDP broadcasts to find and advertise controllers.

@@

\bibitem{dashb0ard:Sebastian Schaffler}
Sebastian Schaffler, Philip Trauner, \emph{dashb0ard}, \url{https://github.com/robot0nfire/dashb0ard},\\ source code,
accessed March 16th 2017

@@

>>>>

\subsection{disc0very}
disc0very\cite{disc0very:Christoph Heiss} is the LAN discovery protocol of fl0w\cite{fl0w:Philip Trauner}. It relies on UDP\cite{UDP:J. Postel} broadcasts to coordinate server and client assignment. Wallaby controller instances as well as the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin edit0r\cite{edit0r:Philip Trauner} utilize it to determine if there is already an active fl0w server on the network upon startup without user interaction.

\subsubsection{Discovery process}
Upon launch disc0very\cite{disc0very:Christoph Heiss} listens for advertisements from an already running fl0w\cite{fl0w:Philip Trauner} server. If an advertisement is received the client-mode is engaged and a connection to the server is established. If no advertisement has been received after 2000ms server-mode is engaged. Server-mode can be disabled for clients that do not have the capability to become a server (for example edit0r\cite{edit0r:Philip Trauner}).

\begin{figure}[H]
\centering
\begin{json}
{
    "address": "<address>",
    "port": "<port>"
}
\end{json}
\caption{disc0very advertisement encoding in JSON\cite{JSON:T. Bray Ed.}}
\label{fig:discovery_advertisement}
\end{figure}

\subsubsection{Error recovery}
disc0very\cite{disc0very:Christoph Heiss} actively listens for advertisements in server-mode to prevent more than one running server on the network. If a server receives an advertisement from another server both shutdown and return to discovery mode.

@@

\bibitem{dashb0ard:Sebastian Schaffler}
Sebastian Schaffler, Philip Trauner, \emph{dashb0ard}, \url{https://github.com/robot0nfire/dashb0ard}, source code,
accessed March 16th 2017

@@

\bibitem{disc0very:Christoph Heiss}
Christoph Heiss, \emph{disc0very}, \url{https://github.com/robot0nfire/fl0w/blob/master/Shared/Disc0very.py},\\ source code, accessed March 30th 2017

\bibitem{UDP:J. Postel}
J. Postel, \emph{UDP}, \url{https://www.ietf.org/rfc/rfc768.txt},\\ request for comment, accessed March 30th 2017
